Fisheries management when quotas are costly to change

### 2014-07-25 manuscripts/manuscript.Rmd
presentation updated

ggplot(harvest_fig3, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")

@@

```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ timeseries + statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  xlab("Penalty size (as fraction of NPV0)")

>>>>

ggplot(harvest_fig3, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")

@@

```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ timeseries + statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") +
  xlab("Penalty size (as fraction of NPV0)")

### 2014-07-25 manuscripts/presentation.Rmd
presentation updated

---
title: "Fisheries management when quotas are costly to change"
date: "07/24/2014"
output: ioslides_presentation

author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig (at) gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK

address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: University of Melbourne, Australia 
  - code: UTK
    address: University of Tennessee, Knoxville

@@

@@

theme_set(theme_tufte())
```

```{r analysis, include=FALSE}
source("components/analysis.R")
```

```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png")}
tuna <- read.csv("components/data/tuna.csv")
ggplot(tuna, aes(year, quota)) + geom_point()
```

@@

$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}, \label{eq:state_equation}$$

@@

$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)$$

@@

Choice of parameters 
--------------------

@@

ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_linetype_discrete(labels=relabel)

@@

ggplot(harvest_fig3, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Stock & Harvest Dynamics")  
```

@@

```{r Figure_4, fig.cap="", dev=c("svg", "png")}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ timeseries + statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  xlab("Penalty size (as fraction of NPV0)")

@@

$$NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

and

$$NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}$$

>>>>

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  ioslides_presentation:
    self_contained: false
    css: components/style.css
    incremental: true

author: |
        Carl Boettiger, Michael Bode, James Sanchirico, 
        Jacob LaRiviera, Alan Hastings, Paul Armsworth

@@

<!-- 
Time: 30 minutes with questions
Presenting at: 2014-12-08 15:10:00 PDT
-->

## Our world is changing

<img src="components/images/global-change.jpg" width="500" style="margin:0px auto;display:block">

<small> Overpeck+ (2011) doi: [10.1126/science.1197869](http://doi.org/10.1126/science.1197869) </small>

## Our policies are not

<img src="components/images/nochange.jpg" width="700">

<small> Alex Wong (Getty Images) </small>

# Why?

## Postulate: policy intertia

> Policies are costly to change

## We're quite good at accounting for _ecological_ dynamics

## Dynamic optimization - Dynamic policies

<small> Reed (1979) [10.1016/0095-0696(79)90014-7](http://doi.org/10.1016/0095-0696(79)90014-7) </small>

## Not so good at _policy_ dynamics

- We account for ecological dynamics but not political ones
- We're not political scientists, we don't know the equations of politics (does anyone?)
- Instead, we can investigate the potential impact that costly adjustments have on optimal policy

@@

theme_set(theme_tufte())
```
```{r analysis, include=FALSE}
source("components/analysis.R")
```

## Bluefin Tuna Quotas, ICCAT

```{r Figure_1, fig.cap="Quota on Blue Fin Tuna Catch", dev=c("svg", "png")}
tuna <- read.csv("components/data/tuna.csv")
ggplot(tuna, aes(year, quota)) + geom_point() + theme_bw()
```

@@

$$N_{t+1} = Z_t \frac{A (N_t - h_t)}{1 + B (N_t - h_t)}$$

@@

$$\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left(\frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)$$

@@

Apples to Apples 
--------------------

@@

ggplot(fees, aes(c2, (npv0-value)/npv0, color=variable)) + 
  geom_line(lwd=1) + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("Penalty coefficient") +
  ylab("Reduction in net present value") + 
  scale_color_discrete(labels=relabel)

@@

ggplot(harvest_fig3, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")
```

@@

```{r Figure_4, fig.cap="", dev=c("svg", "png")}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  coord_cartesian(xlim = c(0, .3)) + 
  facet_wrap(~ timeseries + statistic, scale="free_y") + 
  scale_color_discrete(labels=relabel, name="Penalty function") + 
  scale_fill_discrete(labels=relabel, name="Penalty function") + 
  xlab("Penalty size (as fraction of NPV0)")

@@

$$NPV_i( h_1^* ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} )  \frac{1}{(1+\delta)^t}$$

$$NPV_i( h_0^* ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} )  \frac{1}{(1+\delta)^t}$$
